Extended Data

### 2022-02-23 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd

- stem growth is routinely used to estimate woody productivity (but wood density partially decouples them) [@delpierre_wood_2016 and refs therein]
- stem growth and woody productivity are decoupled from GPP[@delpierre_wood_2016 and refs therein]
- close coordination of budburst and initiation of xylogenesis[@delpierre_temperate_2016]
- start of xylogenesis makes growth possible, but actual growth depends on climate conditions during the growth period

>>>>

- stem growth is routinely used to estimate woody productivity (but wood density partially decouples them) [@delpierre_wood_2016 and refs therein]
- stem growth and woody productivity are decoupled from GPP[@delpierre_wood_2016 and refs therein]
- close coordination of budburst and initiation of xylogenesis[@delpierre_temperate_2016]
- start of xylogenesis makes growth possible, but actual growth depends on climate conditions during the growth period
- probably include some mention of conifers (for whcih more work has been done)
